Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-22 writing/DraftExposurePaper/DraftExposurePaper.Rmd
set chunk options for count plots

```{r}
#Top 2000 storm-county pairs for flooding events during tropical cyclones (since 1996)
flood_exposure <- county_events(counties = my_fips,
                              start_year = 1996, end_year = 2011,
                              event_type = "flood")
flood_2000 <- flood_exposure %>%
        slice(1:2000) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count))
flood_2000$value <- cut(flood_2000$count, c(0, 1, 3, 5, 7, 9, 11, 13, 15), 
                   labels = c("0-1", "2-3", "4-5", "6-7", "8-9", "10-11", "12-13", "14-15"), 
                   include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")
map_flood_2000 <- CountyChoropleth$new(flood_2000)
map_flood_2000$set_zoom(eastern_states)
map_flood_2000$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_flood_2000$title <- "Hits for top 2,000 Storm-County Pairs\nfor Flood Events"
c <- map_flood_2000$render()
```

@@

```{r}
#Top 2000 storm-county pairs for tornado events during tropical cyclones
tornado_exposure <- county_events(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             event_type = "tornado")
tornado_2000 <- tornado_exposure %>%
        slice(1:2000) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count))
tornado_2000$value <- cut(tornado_2000$count, c(0, 1, 3, 5, 7, 9, 11, 13, 15), 
                   labels = c("0-1", "2-3", "4-5", "6-7", "8-9", "10-11", "12-13", "14-15"), 
                   include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")
map_tornado_2000 <- CountyChoropleth$new(tornado_2000)
map_tornado_2000$set_zoom(eastern_states)
map_tornado_2000$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_tornado_2000$title <- "Hits for top 2,000 Storm-County Pairs\nfor Tornado Events"
a <- map_tornado_2000$render()
```

```{r}
#Top 2000 storm-county pairs for wind events during tropical cyclones
wind_exposure <- county_events(counties = my_fips,
                              start_year = 1988, end_year = 2011,
                              event_type = "wind")
wind_2000 <- wind_exposure %>%
        slice(1:2000) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count))
#Or
#wind_2000 <- wind_exposure %>%
        #group_by(fips) %>%
        #summarise(count = n()) %>%
        #arrange(desc(count))
        #slice(1:2000)
        #rename(region = fips) %>%
        #mutate(region = as.numeric(region), count = as.numeric(count))
wind_2000$value <- cut(wind_2000$count, c(0, 1, 3, 5, 7, 9, 11, 13, 15), 
                   labels = c("0-1", "2-3", "4-5", "6-7", "8-9", "10-11", "12-13", "14-15"), 
                   include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")
map_wind_2000 <- CountyChoropleth$new(wind_2000)
map_wind_2000$set_zoom(eastern_states)
map_wind_2000$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_tornado_2000$title <- "Hits for top 2,000 Storm-County Pairs\nfor Wind Events"
b <- map_wind_2000$render()
```

@@

```{r}
tornado_count <- tornado_exposure %>%
              group_by(fips) %>%
              summarise(count = n()) %>%
              rename(region = fips) %>%
              mutate(region = as.numeric(region), count = as.numeric(count))
tornado_count$value <- cut(tornado_count$count, c(0, 5, 8, 12, 15,
                                                    18, 21, 24, 26),
                           labels = c("0-5", "6-8", "9-12", "13-15",
                                      "16-18", "19-21", "22-24", "25-26"),
                           include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")

@@

```{r}
wind_count <- wind_exposure %>%
              group_by(fips) %>%
              summarise(count = n()) %>%
              rename(region = fips) %>%
              mutate(region = as.numeric(region), count = as.numeric(count))
wind_count$value <- cut(wind_count$count, c(0, 5, 8, 12, 15,
                                                    18, 21, 24, 26),
                           labels = c("0-5", "6-8", "9-12", "13-15",
                                      "16-18", "19-21", "22-24", "25-26"),
                           include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")

@@

```{r}
flood_count <- flood_exposure %>%
              group_by(fips) %>%
              summarise(count = n()) %>%
              rename(region = fips) %>%
              mutate(region = as.numeric(region), count = as.numeric(count))
flood_count$value <- cut(flood_count$count, c(0, 5, 8, 12, 15,
                                                    18, 21, 24, 26),
                           labels = c("0-5", "6-8", "9-12", "13-15",
                                      "16-18", "19-21", "22-24", "25-26"),
                           include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")

>>>>

```{r warning = FALSE, message = FALSE, echo = FALSE}
#Top 2000 storm-county pairs for flooding events during tropical cyclones (since 1996)
flood_exposure <- county_events(counties = my_fips,
                              start_year = 1996, end_year = 2011,
                              event_type = "flood")
flood_2000 <- flood_exposure %>%
        slice(1:2000) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count))
flood_2000$value <- cut(flood_2000$count, c(0, 1, 3, 5, 7, 9, 11, 13, 15), 
                   labels = c("0-1", "2-3", "4-5", "6-7", "8-9", "10-11", "12-13", "14-15"), 
                   include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")
map_flood_2000 <- CountyChoropleth$new(flood_2000)
map_flood_2000$set_zoom(eastern_states)
map_flood_2000$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_flood_2000$title <- "Hits for top 2,000 Storm-County Pairs\nfor Flood Events"
c <- map_flood_2000$render()
```

@@

```{r warning = FALSE, message = FALSE, echo = FALSE}
#Top 2000 storm-county pairs for tornado events during tropical cyclones
tornado_exposure <- county_events(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             event_type = "tornado")
tornado_2000 <- tornado_exposure %>%
        slice(1:2000) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count))
tornado_2000$value <- cut(tornado_2000$count, c(0, 1, 3, 5, 7, 9, 11, 13, 15), 
                   labels = c("0-1", "2-3", "4-5", "6-7", "8-9", "10-11", "12-13", "14-15"), 
                   include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")
map_tornado_2000 <- CountyChoropleth$new(tornado_2000)
map_tornado_2000$set_zoom(eastern_states)
map_tornado_2000$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_tornado_2000$title <- "Hits for top 2,000 Storm-County Pairs\nfor Tornado Events"
a <- map_tornado_2000$render()
```

```{r warning = FALSE, message = FALSE, echo = FALSE}
#Top 2000 storm-county pairs for wind events during tropical cyclones
wind_exposure <- county_events(counties = my_fips,
                              start_year = 1988, end_year = 2011,
                              event_type = "wind")
wind_2000 <- wind_exposure %>%
        slice(1:2000) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count))
#Or
#wind_2000 <- wind_exposure %>%
        #group_by(fips) %>%
        #summarise(count = n()) %>%
        #arrange(desc(count))
        #slice(1:2000)
        #rename(region = fips) %>%
        #mutate(region = as.numeric(region), count = as.numeric(count))
wind_2000$value <- cut(wind_2000$count, c(0, 1, 3, 5, 7, 9, 11, 13, 15), 
                   labels = c("0-1", "2-3", "4-5", "6-7", "8-9", "10-11", "12-13", "14-15"), 
                   include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")
map_wind_2000 <- CountyChoropleth$new(wind_2000)
map_wind_2000$set_zoom(eastern_states)
map_wind_2000$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_tornado_2000$title <- "Hits for top 2,000 Storm-County Pairs\nfor Wind Events"
b <- map_wind_2000$render()
```

@@

```{r warning = FALSE, message = FALSE, echo = FALSE}
tornado_count <- tornado_exposure %>%
              group_by(fips) %>%
              summarise(count = n()) %>%
              rename(region = fips) %>%
              mutate(region = as.numeric(region), count = as.numeric(count))
tornado_count$value <- cut(tornado_count$count, c(0, 5, 8, 12, 15,
                                                    18, 21, 24, 26),
                           labels = c("0-5", "6-8", "9-12", "13-15",
                                      "16-18", "19-21", "22-24", "25-26"),
                           include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")

@@

```{r warning = FALSE, message = FALSE, echo = FALSE}
wind_count <- wind_exposure %>%
              group_by(fips) %>%
              summarise(count = n()) %>%
              rename(region = fips) %>%
              mutate(region = as.numeric(region), count = as.numeric(count))
wind_count$value <- cut(wind_count$count, c(0, 5, 8, 12, 15,
                                                    18, 21, 24, 26),
                           labels = c("0-5", "6-8", "9-12", "13-15",
                                      "16-18", "19-21", "22-24", "25-26"),
                           include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")

@@

```{r warning = FALSE, message = FALSE, echo = FALSE}
flood_count <- flood_exposure %>%
              group_by(fips) %>%
              summarise(count = n()) %>%
              rename(region = fips) %>%
              mutate(region = as.numeric(region), count = as.numeric(count))
flood_count$value <- cut(flood_count$count, c(0, 5, 8, 12, 15,
                                                    18, 21, 24, 26),
                           labels = c("0-5", "6-8", "9-12", "13-15",
                                      "16-18", "19-21", "22-24", "25-26"),
                           include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")
